Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
A sentance to a line and specify bibliography

---
title: Meta-analysis of fungicide application timing for powdery mildew management
  in mungbean.
author: "P. Melloy"
date: "31/01/2020"
output:
  html_document: default
---

@@

## Introduction
Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. Mungbean can potentially yield up to 2.3 tonnes per hectare, and worth up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6). Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43%. Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
### Managements strategies
#### and conditions for infection
Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [Kelly et. al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update). In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.
Signs of powdery mildew are almost always first observed when temperatures start to cool.

>>>>

---
title: Meta-analysis of fungicide application timing for powdery mildew management
  in mungbean.
author: "P. Melloy"
date: "31/01/2020"
output:
  html_document: default
bibliography: Mungbean.bib
---

@@

## Introduction
Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. 
Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6). 
Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43% [Kelly et. al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update). 
Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
### Managements strategies
#### and conditions for infection
Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [Kelly et. al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update). In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.
Signs of powdery mildew are almost always first observed when temperatures start to cool.
